A Large-Scale Study of the Use of Eval in R

### 2020-08-24 inst/paper/main.tex
wip

\section{Research Question}
This section presents the results of our empirical study of eval in the R language.
\subsection{How many evals}

In our corpus eval is called \AllAllCallCountRnd{} times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. Table \ref{table:eval-count-summary} shows the number of
calls and callsites for the four kinds of eval functions from core and packages.
The core R packages are the biggest consumers of eval. Majority of calls,
\CoreAllCallCountRnd, originate from the core R packages. Kaggle code, which is
end-user code, has merely \KaggleAllCallCountRnd calls to eval.

@@

Eval is evil, we would like to replace it.
Research Questions
How often is eval used? 
How often it is used in base / other packages?
blocking: cannot find out precisely what comes from base
What is the source of evals?
Provenance (source arguments to eval)
How many evals are in libraries / vignettes
What is eval used for?
??Eval in the tidyverse
TODO: Classification of evals in  packages (Pierre)
TODO: look at the first function to get
binary / unary / assignment / other function
does it have {
evals that do nothing (they get values)
...
TODO: In the case of base package (Filip)
access default values of formals
simply implementation
weird replacement of calls (write.csv -> write.table)
accessing variable from another environment (instead of get)
evaling user input
Change of caller pattern: 
m <- match.call()
 m$name <- NULL
 m[[1L]] <- as.name("library")
eval(m, .GlobalEnv)
     - 	TODO: How dangerous is eval? (Aviral)
Does eval generate new code (create new functions)?
environment writes (reads)
system environment variables
connections
random number generator - setting seed
Does eval do dynamic code loading?
Does eval argument reflect on the call stack?
Calls to C Code
TODO: Could the eval be made safer?
TODO: Could some of the eval calls be replaced?

>>>>

\section{Usage Metrics}

This section presents an overiew of the usage of \eval in our corpus.
Previous work reported that 82\% of JavaScript-enabled web pages used
\eval~\cite{ecoop11}, the case for R is more striking at \miss{100\%} of the
programs use that feature.

This strikingly high number is due to the fact that the language
implementation, the core packages, use \eval extensively. So, in our
analysis, we differentiate \eval based on where they originate from. A {\bf
  core} \eval is one that occurs in the code of a core package.  A {\bf
  dependent} \eval is one that occurs in a package that was included by the
target package. An {\bf own} \eval is one that occurs in the source code of
the target package. We label an \eval occurence as {\bf unknown} when we are
not able to deterimine its origin.\footnote{One source of unknown evals is
  when the \eval function passed as an argument to a higher-order function
  such as \c{lapply}, another is when the code lacks source references.}

Over all, we observed \AllAllCallCountRnd call to \eval in \miss{3,000} runs
of our corpus. The mean number of calls per run was \miss{20} (with a min of
\c{1} and a max of \c{10,000}). Table~\ref{A} details the usage of \eval
across the corpus.  The format is T (m/M/x) where T is the total number of
calls observed for all runs of the corpus, m and x are the minimum and
maximum number of calls for any given run, and A is the mean number of calls
per run.  We can observe \miss{???}. {\bf <The following is a place
  holder. Real text will come once we have the table.>} The majority of
calls come from the core packages.  Kaggle does not have any own calls, any
\eval in those happens in dependent packages and core.

\begin{verbatim}
Table A

         core      dependent   own
----------------------------------------
CRAN   10M?(1/2/3) 1M?(1/2/3) 1K?(1/2/3)
Kaggle 2K?(1/2/3)  1K?(1/2/3) 0 (0/0/0)
\end{verbatim}

The following table will be split up:

@@
